---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"Binomial"` is a [R](http://www.r-project.org/) package that provides functions for calculating probabilities of a Binomial random variable, and related calculations such as the
probability distribution, the expected value, variance, etc.

* `bin_choose()` calculates the number of combinations in which k successes can occur in n trials.
* `bin_probability()` calculates probabilities about the number of successes in a fixed number of random trials performed under identical conditions
* `bin_distribution()` calculates probabilities about different number of successes in a fixed number of random trials performed under identical conditions
* `plot()` method that graphs a barplot to display the probability histogram of a binomial distribution object "bindis".
* `bin_cumulative()` calculates the cumulative probability of successes
* `plot()` graphs the cumulative distribution of object "bincum"
* `bin_variable()` takes in trials and prob and returns a list with trials: number of trials and prob: probability of success.
* `print()` nicely print the content of an object "binvar"
* `summary()` a list of class "summary.binvar" containing named elements (trials,prob,mean,variance,mode,skewness,kurtosis) of an object "binvar"
* `print()` nicely print the content of an object "summary.binvar"


## Motivation

This package has been developed to conveniently calculate probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```{r, eval = FALSE}
# development version from GitHub:
#install.packages("devtools") 

# install "cointoss" (without vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-JingtongZhao/Binomial")
# install "cointoss" (with vignettes)
#devtools::install_github("stat133-sp19/hw-stat133-JingtongZhao/Binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(Binomial)
## Calculating combinations
combination = bin_choose(n = 5, k = 2)
combination

## Calculating probability
probability = bin_probability(success = 2, trials = 5, prob = 0.5)
probability

## Probability distribution
distribution = bin_distribution(trials = 5, prob = 0.5)
distribution

## Plot of probability distribution
plot(distribution)


## Cumulative probability distribution
cumulative = bin_cumulative(trials = 5, prob = 0.5)
cumulative

## Plot of probability distribution
plot(cumulative)

## Binomial Variable
bin1 <- bin_variable(trials = 10, p = 0.3)
summary(bin1)

## Functions of measures
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```








